### 2020-06-11 report/sections/server/extensions/error.tex
Report: complete chapter 6

const onSubscribe = (event) => {
	...
	// Update role-WebSocket mapping.
	roleToSocket[role] = socket;
	socketToRole.set(socket, role);
	waiting.delete(role);
	...
}
\end{lstlisting}
\captionof{lstlisting}{\dots}
\label{lst:cancelconnectsvr}
\end{figure}

@@

\subparagraph{Server endpoint experiences logical error:}
This is when the developer's implementation for the server
endpoint throws an uncaught exception. 
We wrap the runtime EFSM execution methods in
\lstonelinejs{try}/\lstonelinejs{catch}
blocks, and handle the error with a new \texttt{cancel()}
method we generate for the runtime in \fancyname{NodeMPST}.
The \texttt{cancel()} method invokes
the \texttt{close()} method on all browser endpoints,
then executes the user-defined cancellation handler.

Browser endpoints detect this through the \texttt{onclose}
WebSocket event listener. We extend the runtime
generated by \fancyname{ReactMPST} to handle this event
in the corresponding case of a switch statement
defined on the close code, as shown below.

\begin{lstlisting}[language=javascript,tabsize=2]
private onClose({ code, reason }: CloseEvent) {
	switch (code) {
		case Cancellation.Receive.NORMAL: {
			// Normal, clean cancellation
			return;
		}
		case Cancellation.Receive.SERVER_DISCONNECT: {
			// Server role disconnected
			this.processCancellation(Roles.Server, 'server disconnected')
			return;
		}
		case Cancellation.Receive.CLIENT_DISCONNECT: { ... }
		case Cancellation.Receive.LOGICAL_ERROR: { ... }
		default: { ... }
	}
}
\end{lstlisting}

\begin{lstlisting}[language=javascript,tabsize=2]
private processCancellation(role: Roles.All, reason?: any) {
	const cancelUI = ...
	this.setState({
		elem: this.props.cancellation(role, reason !== undefined ? String(reason) : reason),
        });
    }
\end{lstlisting}

@@

\subparagraph{Browser endpoint experiences logical error:}
% emit event to server
% server needs to propagate cancellation
% other browser endpoints receive in the same wayy

@@

Traditionally, this will throw an error. However,
the semantics of cancellation should dominate any asynchronous
operations from the developer, so we need to work around
the lack of pre-emption. We do this by defining a custom
error handler for the WebSocket send action: in short,
if a send action fails, and it is due to the session
being cancelled prior, then there is nothing to worry about.

>>>>

const onSubscribe = (event) => {
	...
	// Update role-WebSocket mapping.
	roleToSocket[role] = socket;
	socketToRole.set(socket, role);
	waiting.delete(role);
	...
}
\end{lstlisting}
\captionof{lstlisting}{Modified Connection Management in
Server Endpoint with Cancellation}
\label{lst:cancelconnectsvr}
\end{figure}

@@

\subparagraph{Server endpoint experiences logical error:}
This is when the developer's implementation for the server
endpoint throws an uncaught exception. 
We wrap the runtime EFSM execution methods in
\lstonelinejs{try}/\lstonelinejs{catch}
blocks, and handle the error with a \texttt{cancel()}
method we generate for the runtime in \fancyname{NodeMPST}.
The \texttt{cancel()} method invokes
the \texttt{close()} method on all browser endpoints,
then executes the user-defined cancellation handler.

Browser endpoints detect this through the \texttt{onclose}
WebSocket event listener. We extend the runtime
generated by \fancyname{ReactMPST} to handle this event
in the corresponding case of a switch statement
defined on the close code, 
as shown in \cref{lst:canceloncloseclient}.

\begin{figure}[!h]
\begin{lstlisting}[language=javascript,tabsize=2]
private onClose({ code, reason }: CloseEvent) {
	switch (code) {
		case Cancellation.Receive.NORMAL: { ... }
		case Cancellation.Receive.SERVER_DISCONNECT: {
			// Server role disconnected
			this.processCancellation(Roles.Server, 'server disconnected')
			return;
		}
		case Cancellation.Receive.CLIENT_DISCONNECT: { ... }
		case Cancellation.Receive.LOGICAL_ERROR: { ... }
		default: { ... }
	}
}
\end{lstlisting}
\captionof{lstlisting}{WebSocket Close Event Listener in
Browser Endpoints}
\label{lst:canceloncloseclient}
\end{figure}

Browser endpoints process the session cancellation
by simply rendering the UI element generated
by the user-supplied session cancellation handler.

\begin{lstlisting}[language=javascript,tabsize=2]
private processCancellation(role: Roles.All, reason?: any) {
	this.setState({
		elem: this.props.cancellation(role, reason);
	});
}
\end{lstlisting}

@@

\subparagraph{Browser endpoint experiences logical error:}
This is when the developer's implementation for the browser
endpoint throws an uncaught exception. 
The runtime for the browser endpoint will catch
the exception and emit the cancellation to the server
using the corresponding close code.

The server endpoint will detect the cancellation event
using an \texttt{onclose} WebSocket event listener
similar to that defined in \cref{lst:canceloncloseclient},
Then, the server propagates the cancellation
to the other endpoints.
We present the propagation implementation
in \cref{lst:cancelpropagate}.
The ``payload'' of the propagated cancellation is also structured
as an object with the role and reason as properties,
so the browser endpoint can parse and handle using
the same framework presented in \cref{lst:canceloncloseclient}.
After propagating the cancellation to other endpoints,
runtime invokes the user-defined session cancellation
handler, then \textit{restarts} the runtime to accept
new connections once again. 
Any exceptions thrown by the developer's session cancellation
handler will be ignored.

\begin{figure}[!h]
\begin{lstlisting}[language=javascript,tabsize=2]
private propagateCancellation(cancelled: Roles.Peers, reason?: any)
{
	// Construct cancellation message as object
	// with role and reason as properties
	const message = Cancellation.toChannel(cancelled, reason);

	// Emit cancellation to other roles
	Object.entries(this.roleToSocket)
		.filter(([role, _]) => role !== cancelled)
		.forEach(([_, socket]) => {
			socket.removeAllListeners();
			socket.close(Cancellation.Emit.LOGICAL_ERROR,
				JSON.stringify(message));
		});

	try {
		// Execute user-defined cancellation handler
		const doCancel = this.cancellation(cancelled, reason);
		if (doCancel instanceof Promise) {
			doCancel.then(this.restart).catch(this.restart);		
		} else {
			this.restart();
		}
	} catch {
		this.restart();
	}
}
\end{lstlisting}
\captionof{lstlisting}{Propagating Session Cancellation Events in
Server Endpoint}
\label{lst:cancelpropagate}
\end{figure}

@@

Traditionally, this will throw an error. However,
the semantics of cancellation should dominate any asynchronous
operations from the developer, so we need to work around
the lack of pre-emption. We do this by defining a custom
error handler for the WebSocket send action: in short,
if a send action fails due to the session
being cancelled prior, then there is nothing to worry about.
